\documentclass[12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[a4paper, margin=1in]{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{hyperref}

\titleformat{\section}{\large\bfseries}{\thesection.}{1em}{}

\title{\textbf{Game Experience Questionnaire}}
\author{}
\date{}

\begin{document}

\maketitle
\hrule
\vspace{0.5cm}

\section*{Instructions}
Please indicate the extent to which you agree with each statement below by circling a number from 1 (Strongly Disagree) to 5 (Strongly Agree).

\vspace{0.5cm}

\begin{center}
\begin{tabular}{|c|c|}
\hline
1 & Strongly Disagree \\
\hline
2 & Disagree \\
\hline
3 & Neutral \\
\hline
4 & Agree \\
\hline
5 & Strongly Agree \\
\hline
\end{tabular}
\end{center}

\vspace{0.5cm}
\hrule
\vspace{0.5cm}

\section*{1. Basic Attention}

\begin{enumerate}[label=\arabic*.]
  \item The game held my attention.
  \item I was focused on the game.
  \item I put effort into playing the game.
  \item I felt that I was trying my best.
\end{enumerate}

\section*{2. Temporal Dissociation}

\begin{enumerate}[resume]
  \item I lost track of time while playing.
  \item I was consciously aware of the real world while playing. \textit{(reverse-scored)}
  \item I forgot about my everyday concerns.
  \item I was aware of myself in my surroundings. \textit{(reverse-scored)}
  \item I noticed events taking place around me. \textit{(reverse-scored)}
  \item I felt the urge to stop playing and check what was happening around me. \textit{(reverse-scored)}
\end{enumerate}

\section*{3. Transportation}

\begin{enumerate}[resume]
  \item I felt separated from the real-world environment.
  \item The game felt like an experience rather than an activity.
  \item My sense of being in the game was stronger than in the real world.
  \item I became so involved I forgot I was using controls.
  \item I felt like I was moving through the game according to my own will.
\end{enumerate}

\section*{4. Emotional Involvement}

\begin{enumerate}[resume]
  \item I felt emotionally attached to the game.
  \item I was interested in how the game’s events would progress.
  \item I was interested in reaching the ending or final state of the simulation.
  \item I felt so involved that I wanted to speak to the game directly.
\end{enumerate}

\section*{5. Enjoyment}

\begin{enumerate}[resume]
  \item I enjoyed the game’s chat.
  \item I enjoyed playing the game.
  \item I would like to play the game again.
\end{enumerate}

\section*{6. Character Coherence}

\begin{enumerate}[resume]
    \item A character said something that did not match their established personality or tone. \textit{(reverse-scored)}
    \item A character maintained a consistent personality.
    \item A character behaved in an unnaturally calm, logical, or exaggerated way, which felt awkward. \textit{(reverse-scored)}
    \item A character appropriately understood the intent behind my actions or dialogue.
    \item A character's behavior or emotions did not align with what had previously occurred. \textit{(reverse-scored)}
    \item Out-of-place or incoherent character behavior occurred so frequently that it disrupted my immersion. \textit{(reverse-scored)}
    \item A character's behavior or dialogue reduced emotional immersion (e.g., broke tension or made it harder to empathize). \textit{(reverse-scored)}
    \item A specific line or behavior made me less interested in what would happen next in the game. \textit{(reverse-scored)}
\end{enumerate}

\end{document}
